CrypTool Script\footnote{ Background reading for the CrypTool program}\\ Mathematics and Cryptography

### 2003-04-22 script/en/chapters/primes.tex
be updates

Mersenne claimed that $2^{67}-1$ is a prime number. There is also a mathematical
history behind this claim: it first took over 200 years before \index{Lucas
  Edouard} Edouard Lucas (1842-1891) proved that this number is composite.
However, he argued indirectly and did not name any of the factors. Then Frank
Nelson showed in 1903 which factors make up this composite number: 
$$ 2^{67} -1
=147, 573, 952, 589, 676, 412, 927 = 193, 707, 721 \cdot 761, 838, 257, 287. $$
He admitted to having worked 20 years on the factorisation 
\index{factorisation} (expression as a product of prime factors)\footnote{%
Using CrypTool\index{CrypTool} v1.3 you can factorize numbers in the 
following way: menu {\bf Indiv. Procedures \textbackslash{} RSA Demonstration 
\textbackslash{} Factorisation of a Number}.
}
of this 21-digit decimal number!

@@

\item Polynomial functions $f(x) = a_n x^n + a_{n-1}x^{n-1} + \cdots + a_1 x^1 +
a_0$  ($a_i$ in ${\mathbb Z}$, $n \geq 1$):

>>>>

Mersenne claimed that $2^{67}-1$ is a prime number. There is also a mathematical
history behind this claim: it first took over 200 years before \index{Lucas
  Edouard} Edouard Lucas (1842-1891) proved that this number is composite.
However, he argued indirectly and did not name any of the factors. Then Frank
Nelson showed in 1903 which factors make up this composite number: 
$$ 2^{67} -1
=147, 573, 952, 589, 676, 412, 927 = 193, 707, 721 \cdot 761, 838, 257, 287. $$
He admitted to having worked 20 years on the factorisation 
\index{Factorisation} (expression as a product of prime factors)\footnote{%
Using CrypTool\index{CrypTool} v1.3 you can factorize numbers in the 
following way: menu {\bf Indiv. Procedures \textbackslash{} RSA Demonstration 
\textbackslash{} Factorisation of a Number}.
}
of this 21-digit decimal number!

@@

\newpage
\item Polynomial functions $f(x) = a_n x^n + a_{n-1}x^{n-1} + \cdots + a_1 x^1 +
a_0$  ($a_i$ in ${\mathbb Z}$, $n \geq 1$):
